Descriptive stats and visuals

### 2020-09-08 dev/hmm_grein.Rmd
First results on real data

#make_stancode_hmm(m1)
#xx <- brms::make_standata(m1$formula, data = make_data_hmm(m1)$brmsdata)
m1_fit <- brmhmm(m1, cache_file = paste0(cache_dir,"/grein_m1.rds"))

>>>>

make_stancode_hmm(m1)
#xx <- brms::make_standata(m1$formula, data = make_data_hmm(m1)$brmsdata)
m1_fit <- brmhmm(m1, cache_file = paste0(cache_dir,"/grein_m1.rds"))

### 2020-09-08 dev/raw_data_preprocessing.Rmd
More preprocessing, descriptive statistics
First results on real data

TODO: code adverse events, code discontinued_medication_reason

@@

Check values for all markers with converted units

```{r}
for(conversion in unit_conversions) {
  for(marker_to_check in conversion$markers) {
    cat(" ==== ", marker_to_check, "=====\n")
    complete_data$marker_data %>% filter(marker == marker_to_check, !is.na(value)) %>% 
      pull(value) %>% unique() %>% print()
    print(
      complete_data$marker_data %>% filter(marker == marker_to_check, !is.na(value)) %>% 
        ggplot(aes(x = value)) + geom_histogram() + facet_wrap(marker ~ unit, scales = "free")
    )
  }
}
```

@@

```{r}
i <- 2; j <- 3
for(i in 1:(length(hospital_data) - 1)) {
  for(j in (i + 1):length(hospital_data)) {
    #cat(i,",", j,"\n")

>>>>

TODO: code adverse events, code discontinued_medication_reason
TODO: check last day, add outcome to breathing data, possibly

@@

Check values for all markers with converted units (Note the 0 for Amoxiclav has been checked and is in the original data as well)

```{r}
for(conversion in unit_conversions) {
  for(marker_to_check in conversion$markers) {
    cat(" ==== ", marker_to_check, "=====\n")
    complete_data$marker_data %>% filter(marker == marker_to_check, !is.na(value)) %>% 
      pull(value) %>% unique() %>% print()
    print(
      complete_data$marker_data %>% filter(marker == marker_to_check, !is.na(value)) %>% 
        ggplot(aes(x = value)) + geom_histogram() + facet_wrap(marker ~ unit, scales = "free")
    )
  }
}
```
```{r}
complete_data$marker_data %>% filter(marker == "amoxiclav", value == 0)
```

@@

```{r}
for(i in 1:(length(hospital_data) - 1)) {
  for(j in (i + 1):length(hospital_data)) {
    #cat(i,",", j,"\n")

### 2020-09-08 manuscript/descriptive.Rmd
First results on real data

```{r}
disease_levels <- c("Discharged", breathing_levels, "Death")
outcome_data <- data$patient_data %>% 
  filter(outcome %in% c("Discharged", "Death")) %>%
  transmute(patient_id = patient_id, 
            hospital_id = hospital_id,
            day = last_record,
            breathing = as.character(outcome))

data_for_plot <- data$breathing_data %>% 
  mutate(breathing = as.character(breathing)) %>%
  rbind(outcome_data) %>%
  mutate(breathing = factor(breathing, levels = disease_levels, ordered = TRUE))

data_for_plot %>% ggplot(aes(x = day, y = patient_id, fill = breathing)) + 
  geom_tile() + 
  scale_fill_viridis_d(direction = -1) +
  theme(axis.text.y = element_blank())
```
```{r}

@@

>>>>

```{r}
# disease_levels <- c("Discharged", breathing_levels, "Death")
# outcome_data <- data$patient_data %>% 
#   filter(outcome %in% c("Discharged", "Death")) %>%
#   transmute(patient_id = patient_id, 
#             hospital_id = hospital_id,
#             day = last_record,
#             breathing = as.character(outcome))
#                                                 
# data_for_plot <- data$breathing_data %>% 
#   mutate(breathing = as.character(breathing)) %>%
#   rbind(outcome_data) %>%
#   mutate(breathing = factor(breathing, levels = disease_levels, ordered = TRUE))
# 
# if(any(is.na(data_for_plot$day)) || any(is.na(data_for_plot$breathing))) {
#   stop("Problem")
# }

data$breathing_data %>% ggplot(aes(x = day, y = patient_id, fill = breathing)) + 
  geom_tile() + 
  scale_fill_viridis_d(direction = -1) +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~hospital_id, scales = "free")

```
```{r}
data$breathing_data %>% group_by(hospital_id, patient_id) %>%
  summarise(first = min(day, na.rm = TRUE)) %>%
  filter(first > 0)
```

```{r}
wide <- prepare_marker_data_wide(data)
wide  %>% ggplot(aes(x = day, y = patient_id, fill = took_convalescent_plasma)) + 
  geom_tile() + 
  scale_fill_viridis_d(direction = -1) +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~hospital_id, scales = "free")

wide  %>% ggplot(aes(x = day, y = patient_id, fill = breathing)) + 
  geom_tile() + 
  scale_fill_viridis_d(direction = -1) +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~hospital_id, scales = "free")

@@

```{r}
outcome_data %>% filter(day > 30)
data$patient_data %>% filter(patient_id == "kOw52xii4l")
data_for_plot %>% filter(is.na(day))
```
```{r}
data$patient_data %>% filter(is.na(last_record))
```

```{r}
data$patient_data %>% group_by(hospital_id) %>% summarise(count = n())
```
Where do we have measurements for the individual markers (tiles show where we have breathing data, study sites are coded via fill color, crosses show available data).
```{r}
all_markers <- data$marker_data %>% group_by(marker) %>% summarise(n_obs = n(), .groups = "drop") %>%
  arrange(desc(n_obs)) %>% filter(n_obs > 10) %>% pull(marker)

breathing_data_ordered <- data$breathing_data %>%  mutate(patient_id = factor(patient_id) %>% fct_reorder(hospital_id, .fun = unique))

n_markers <- length(all_markers)
step_size <- 4
for(i in 1:ceiling(n_markers / step_size)) {
  markers_to_show <- all_markers[((i - 1) * step_size + 1):min(n_markers, i * step_size)]
  print(
    data$marker_data %>%
      filter(marker %in% markers_to_show)  %>%
      ggplot(aes(x = day, y = patient_id)) +
        geom_tile(data = breathing_data_ordered, aes(fill = hospital_id)) +
        geom_point(shape = "cross") +
        theme(axis.text.y = element_blank()) +
        scale_fill_brewer(type = "qual", palette = 2, guide = FALSE) +
        facet_wrap(~marker, nrow = 1, scales = "free_x")

  )
}
```
